Demand-aware geo-distributed placement for low latency

### 2015-07-05 auspice/eval.tex
added abstract, small reference fixes in rest of thesis.

%Our main goal is to quantify the benefits and costs of the choices in \auspice's distributed design---our main contribution---with respect to the subset of design goals  ($\S$\ref{sec:design_goals}) that are quantifiable, namely client-perceived latency benefit and provider-perceived update cost under high mobility. We use the implemented prototype to evaluate (1) \auspice's replication strategies against simple ones used by DNS providers today as well as DHT-based alternatives proposed in research, and (2) a deployment of \auspice\ against several commercial managed DNS providers in live operation. We use simulations to evaluate (3) the sensitivity of \auspice's benefits with respect to mobile workload parameters, and (4) the scalability of \auspice\ to regimes beyond those permitted by our testbeds. We do not attempt to evaluate \auspice's functional design goals---resilience to failures, consistency, extensibility, security---except to the extent that all experiments subsume the overhead of these features.

@@

\textbf{Workload:} There is no real workload today of clients querying a name service in order to communicate with mobile devices frequently moving across different network addresses, both because such a name service does not exist and mobile devices do not have publicly visible IP addresses. So we conduct an evaluation using synthetic workloads for device names ($\S$\ref{sec:comparison}), but to avoid second-guessing future workload patterns, we conduct a comprehensive sensitivity analysis against all of the relevant parameters such as the read rate, write rate, popularity, and geo-locality of demand \cite{techreport}.

@@

The following are default experimental parameters %(except for $\S$\ref{sec:sensitivity} on sensitivity analysis) 
for {\em device names}. The ratio of the total number of lookups across all devices to the total number of updates is 1:1, i.e., devices are queried for on average as often as they change addresses. The lookup rate of any single device name is uniformly distributed between 0.5--1.5$\times$ the average lookup rate; the update rate is similarly distributed and drawn independently.%, so there is no correlation between the lookup and update rate of a name.

\rmCR{
\begin{table}[t]
\centering
\small{
\begin{tabular}{c|c}
{\bf Workload parameter} & {\bf Value} \\ \hline
Fraction of (highly mobile) device names & 90\%  \\ \hline
Fraction of (mostly static) service names & 10\%   \\ \hline
\% of device name lookups   & 33.33\%  \\ \hline
\% of device name updates  & 33.33\% \\ \hline
\% of service name lookups   & 33.33\%  \\ \hline
\% of service name updates  & 0.01\% \\ \hline
Geo-locality: [devices, services] & [0.75, 0.8]  \\ \hline
\end{tabular}
}
\caption{Default workload parameters. %(except $\S$\ref{sec:sensitivity}).
}
\vspace{-0.15in}
\label{tab:setup}
\end{table}
}

\begin{figure*}[t]
\subfigure[Lookup latencies (load = 0.3)]{\label{fig:namesquerymediancdf}\includegraphics[scale=0.55]{graph/newgraphs/lookup-latency-cdf.pdf}}
\subfigure[Lookup latency vs. load]{\label{fig:load}\includegraphics[scale=0.55]{graph/newgraphs/load-latency.pdf}}
\subfigure[Update cost vs. load]{\label{fig:loadupdatecost}\includegraphics[scale=0.55]{graph/newgraphs/load-updatecost.pdf}}
%\subfigure[Update cost]{\label{fig:updatebw}\includegraphics[scale=0.55]{graph/newgraphs/cdf-update-cost.pdf}}
\vspace{-0.15in}
\caption{\small{\auspice\ has up to 5.7$\times$ to 9$\times$ lower latencies than \staticthree\ and \codons\ reps. (\ref{fig:load}). A load of 1 means 200 lookups/sec and 100 updates/sec per name server. \replicateall\ peaks out at a load of 0.3 while \auspice\ can sustain a request load of up to 8 as it carefully chooses between 3 and 80 replicas per name.}}
\vspace{-0.15in}
\label{fig:lookupupdate}
\end{figure*}

@@

{\textbf{Replication schemes compared:}}
%\label{sec:schemes}
\textbf{\auspice} uses the replica placement strategy as described in $\S$\ref{sec:design} with the default parameter values $F=3, \mu = 0.7, \nu = 0.5$. %We set the replication control parameter ($\beta$)  to ensure that the utilization of the servers remains below  70\% (refer to Equation \ref{eq:mu}). 
We compare \auspice\ against the following: (1) \textbf{\staticthree} replicates each name at three random locations; (2) \textbf{\replicateall} replicates all names at all locations; (3) \textbf{\codons} replicates names using consistent hashing with replication similar to Codons\cite{codons-paper}. The number of replicas is chosen based on the popularity ranking of a name and  the location of replicas is decided by consistent hashing. The average hop count in Codons's underlying Beehive algorithm  is set so that it creates the same average number of replicas as \auspice\ for a fair comparison. All schemes direct a lookup to the closest available replica after the first request.

@@

\begin{figure*}[t]
\subfigure[E2E time-to-connect]{\label{fig:ttc_msocket}\includegraphics[width=2.4in,height=1.8in]{graph/camera-ready/connect-time-msocket.pdf}}
\subfigure[Simultaneous mobility]{\label{fig:SimulMig}\includegraphics[width=2.5in, height=1.8in]{figure/SimulMig.pdf}}
\subfigure[Context-aware delivery]{\label{fig:5MemberTimeline}\includegraphics[width=2in, height=1.8in]{figure/5MemTimeLineUsed.pdf}}
\vspace{-0.2in}
\caption{(a) Time-to-connect$\approx$lookup latency for moderate mobility rates ($<\frac{1}{10s}$)  as \auspice\ returns up-to-date responses w.h.p., but sharply rises thereafter (Eq. \ref{eq:ttc}); (b) Simultaneous mobility recovery in $\approx$2 RTTs after both endpoints resurface; (c) Context-aware delivery showing 3 messages  geo-cast to 5 members.}
\vspace{-0.1in}
\label{fig:end2end}
\end{figure*}

@@

The {\em client-perceived update latency}, i.e., the time from when when a client sends an update to when it receives a confirmation. %with total write ordering is shown in Figure \ref{fig:updates}.  
These numbers are measured from the experiment in $\S$\ref{sec:lookup} for load=0.3. The median and 90th percentile update latency for \auspice\ with total write ordering is 284ms and is comparable to other schemes. A request, after arriving an active replica, takes four one-way network delays (two rounds) to be committed by Paxos. The median update latency is a few hundred milliseconds for all schemes as it is dominated by update propagation delays.

The {\em update propagation delay}, i.e., the time from when a client issued a write till the last replica executes the write, is a key determiner of the time-to-connect. As shown in $\S$\ref{sec:scalability}, with eventual consistency, update propagation takes one round, while with total write ordering, update propagation takes two rounds and 50\% more messages.

@@

\blue{
In the next experiment, we show how \auspice\ can choose the epoch length and reconfiguration trigger so as to limit the overhead of reconfiguration (as in $\S$\ref{sec:reconf_policy}) while being responsive to changes in demand geo-locality. The workload changes the geo-distribution of demand for each name every 300 sec. 
For each name, we change the regions from which most requests arise so that changing the placement of replicas becomes necessary to minimize lookup latencies. The experiment is performed on a local cluster with a workload of 1000 names with characteristics as described in Table \ref{tab:setup}. 
The epoch length of group changes is chosen to be 75 sec, which ensures that group changes result in less than 10\% overhead to the system ($\S$\ref{sec:reconf_policy}). 
}

\blue{
We show the lookup latencies of \auspice\ and the message overhead of reconfiguration in the experiment in Figue \ref{fig:latency-time}.   We find that \auspice\ takes two epochs to infer a change in the geo-distribution of demand and to adapt to it.  This result suggests that \auspice\ can optimize lookup latencies provided the geo-distribution of demand for a name remains stable for a few epochs.
Further, we measured the overhead of reconfiguration messages in this experiment to be 3.6\%. The overhead is less than the expected overhead of 10\% because not all names are reconfigured in every epoch. 
%This finding shows that choosing epoch lengths as per the analysis in  Section \ref{sec:gc-analysis} keeps the overhead of group changes to a small fraction of the overall system load.
}
}

>>>>

%Our main goal is to quantify the benefits and costs of the choices in \auspice's distributed design---our main contribution---with respect to the subset of design goals  (Section \ref{sec:design_goals}) that are quantifiable, namely client-perceived latency benefit and provider-perceived update cost under high mobility. We use the implemented prototype to evaluate (1) \auspice's replication strategies against simple ones used by DNS providers today as well as DHT-based alternatives proposed in research, and (2) a deployment of \auspice\ against several commercial managed DNS providers in live operation. We use simulations to evaluate (3) the sensitivity of \auspice's benefits with respect to mobile workload parameters, and (4) the scalability of \auspice\ to regimes beyond those permitted by our testbeds. We do not attempt to evaluate \auspice's functional design goals---resilience to failures, consistency, extensibility, security---except to the extent that all experiments subsume the overhead of these features.

@@

\textbf{Workload:} There is no real workload today of clients querying a name service in order to communicate with mobile devices frequently moving across different network addresses, both because such a name service does not exist and mobile devices do not have publicly visible IP addresses. So we conduct an evaluation using synthetic workloads for device names (Section \ref{sec:comparison}), but to avoid second-guessing future workload patterns, we conduct a comprehensive sensitivity analysis against all of the relevant parameters such as the read rate, write rate, popularity, and geo-locality of demand \cite{techreport}.

@@

The following are default experimental parameters %(except for Section \ref{sec:sensitivity} on sensitivity analysis) 
for {\em device names}. The ratio of the total number of lookups across all devices to the total number of updates is 1:1, i.e., devices are queried for on average as often as they change addresses. The lookup rate of any single device name is uniformly distributed between 0.5--1.5$\times$ the average lookup rate; the update rate is similarly distributed and drawn independently.%, so there is no correlation between the lookup and update rate of a name.

\rmCR{
\begin{table}[t]
\centering
\small{
\begin{tabular}{c|c}
{\bf Workload parameter} & {\bf Value} \\ \hline
Fraction of (highly mobile) device names & 90\%  \\ \hline
Fraction of (mostly static) service names & 10\%   \\ \hline
\% of device name lookups   & 33.33\%  \\ \hline
\% of device name updates  & 33.33\% \\ \hline
\% of service name lookups   & 33.33\%  \\ \hline
\% of service name updates  & 0.01\% \\ \hline
Geo-locality: [devices, services] & [0.75, 0.8]  \\ \hline
\end{tabular}
}
\caption{Default workload parameters. %(except Section \ref{sec:sensitivity}).
}
\vspace{-0.15in}
\label{tab:setup}
\end{table}
}

\begin{figure*}[t]
\subfigure[Lookup latencies (load = 0.3)]{\label{fig:namesquerymediancdf}\includegraphics[scale=0.5]{graph/newgraphs/lookup-latency-cdf.pdf}}
\subfigure[Lookup latency vs. load]{\label{fig:load}\includegraphics[scale=0.5]{graph/newgraphs/load-latency.pdf}}
\subfigure[Update cost vs. load]{\label{fig:loadupdatecost}\includegraphics[scale=0.5]{graph/newgraphs/load-updatecost.pdf}}
%\subfigure[Update cost]{\label{fig:updatebw}\includegraphics[scale=0.55]{graph/newgraphs/cdf-update-cost.pdf}}
\caption{\small{\auspice\ has up to 5.7$\times$ to 9$\times$ lower latencies than \staticthree\ and \codons\ reps. (\ref{fig:load}). A load of 1 means 200 lookups/sec and 100 updates/sec per name server. \replicateall\ peaks out at a load of 0.3 while \auspice\ can sustain a request load of up to 8 as it carefully chooses between 3 and 80 replicas per name.}}
\vspace{-0.15in}
\label{fig:lookupupdate}
\end{figure*}

@@

{\textbf{Replication schemes compared:}}
%\label{sec:schemes}
\textbf{\auspice} uses the replica placement strategy as described in Section \ref{sec:design} with the default parameter values $F=3, \mu = 0.7, \nu = 0.5$. %We set the replication control parameter ($\beta$)  to ensure that the utilization of the servers remains below  70\% (refer to Equation \ref{eq:mu}). 
We compare \auspice\ against the following: (1) \textbf{\staticthree} replicates each name at three random locations; (2) \textbf{\replicateall} replicates all names at all locations; (3) \textbf{\codons} replicates names using consistent hashing with replication similar to Codons\cite{codons-paper}. The number of replicas is chosen based on the popularity ranking of a name and  the location of replicas is decided by consistent hashing. The average hop count in Codons's underlying Beehive algorithm  is set so that it creates the same average number of replicas as \auspice\ for a fair comparison. All schemes direct a lookup to the closest available replica after the first request.

@@

\begin{figure*}[t]
\subfigure[E2E time-to-connect]{\label{fig:ttc_msocket}\includegraphics[width=2.4in,height=1.8in]{graph/camera-ready/connect-time-msocket.pdf}}
\subfigure[Simultaneous mobility]{\label{fig:SimulMig}\includegraphics[width=2.5in, height=1.8in]{figure/SimulMig.pdf}}
\subfigure[Context-aware delivery]{\label{fig:5MemberTimeline}\includegraphics[width=2in, height=1.8in]{figure/5MemTimeLineUsed.pdf}}
\caption{(a) Time-to-connect$\approx$lookup latency for moderate mobility rates ($<\frac{1}{10s}$)  as \auspice\ returns up-to-date responses w.h.p., but sharply rises thereafter (Eq. \ref{eq:ttc}); (b) Simultaneous mobility recovery in $\approx$2 RTTs after both endpoints resurface; (c) Context-aware delivery showing 3 messages  geo-cast to 5 members.}
\label{fig:end2end}
\end{figure*}

@@

The {\em client-perceived update latency}, i.e., the time from when when a client sends an update to when it receives a confirmation. %with total write ordering is shown in Figure \ref{fig:updates}.  
These numbers are measured from the experiment in Section \ref{sec:lookup} for load=0.3. The median and 90th percentile update latency for \auspice\ with total write ordering is 284ms and is comparable to other schemes. A request, after arriving an active replica, takes four one-way network delays (two rounds) to be committed by Paxos. The median update latency is a few hundred milliseconds for all schemes as it is dominated by update propagation delays.

The {\em update propagation delay}, i.e., the time from when a client issued a write till the last replica executes the write, is a key determiner of the time-to-connect. As shown in Section \ref{sec:scalability}, with eventual consistency, update propagation takes one round, while with total write ordering, update propagation takes two rounds and 50\% more messages.

@@

\blue{
In the next experiment, we show how \auspice\ can choose the epoch length and reconfiguration trigger so as to limit the overhead of reconfiguration (as in Section \ref{sec:reconf_policy}) while being responsive to changes in demand geo-locality. The workload changes the geo-distribution of demand for each name every 300 sec. 
For each name, we change the regions from which most requests arise so that changing the placement of replicas becomes necessary to minimize lookup latencies. The experiment is performed on a local cluster with a workload of 1000 names with characteristics as described in Table \ref{tab:setup}. 
The epoch length of group changes is chosen to be 75 sec, which ensures that group changes result in less than 10\% overhead to the system (Section \ref{sec:reconf_policy}). 
}

\blue{
We show the lookup latencies of \auspice\ and the message overhead of reconfiguration in the experiment in Figue \ref{fig:latency-time}.   We find that \auspice\ takes two epochs to infer a change in the geo-distribution of demand and to adapt to it.  This result suggests that \auspice\ can optimize lookup latencies provided the geo-distribution of demand for a name remains stable for a few epochs.
Further, we measured the overhead of reconfiguration messages in this experiment to be 3.6\%. The overhead is less than the expected overhead of 10\% because not all names are reconfigured in every epoch. 
%This finding shows that choosing epoch lengths as per the analysis in  Section \\ref{sec:gc-analysis} keeps the overhead of group changes to a small fraction of the overall system load.
}
}

### 2015-07-05 auspice/implementation.tex
added abstract, small reference fixes in rest of thesis.

We have implemented a prototype of the global name service with support for all of the functions described in Section \ref{sec:MF} using \auspice. A service in \auspice\ is a resolver for a name (or GUID). Each resolver is replicated with primary and active replicas and the number and locations of these replicas is determined by the mapper. We have implemented both uncoordinated, heuristic algorithms as well as the coordinated, optimal placement algorithms as described in the previous two sections.

The name service ensures sequential consistency for each resolution service by establishing a total order across all writes to attributes keyed by the service's GUID. When an active replica receives a write to any GUID attribute, it initiates Paxos (unrelated to Paxos between primaries for placement decisions as in Section \ref{sec:design}) and gets all other active replicas responsible for that GUID to agree on a sequence number for that write. A read request at a replica sees the result of the most recent committed write at that replica. A total ordering of writes at all replicas is insufficient to ensure the desirable property that replicas will {eventually} return the most current (in real time) network address of a mobile device  if no further updates take place (e.g., a mobile may issue an update at replica A and subsequently an update at replica B, but it is theoretically possible for the system to commit the latter before the former). To ensure this property in single-writer scenarios, a client includes a client-local sequence number to each write and the acceptors in Paxos ensure that they do not accept a proposed sequence number for a write $w_1$ if they have already accepted a write $w_2$ with a higher client-local sequence number, thereby causing the proposed write $w_1$ to fail to commit.

@@

%Some parts of the implementation are work in progress at this point. (1) Replica-controllers estimate  geo-distribution of requests based on local name servers' report of the number of lookups received by them; we plan to integrate an IP geo-location database for active replicas instead to report the request geo-distribution to replica-controllers.  (2) A local name server maintains load-induced latency estimates for each name server by querying them for their current load every 5 mins instead of tracking load-induced latency at name servers based on response time of past lookups  as described in $\S$\ref{sec:routing_client_requests}.

%\textbf{Evaluation version:} We have implemented a full-featured prototype of \auspice\ as described above, but our evaluation uses an earlier stable version of our code with some differences.  This evaluation version is implemented in Java with 22K lines of code, and is currently deployed  on Amazon EC2 for users to query via HTTP \cite{gnrswebsite}. This version differs from the described design as follows: (1) An update involves the set of message exchanges described in $\S$$\ref{sec:consistency}$ without assigning any update sequence numbers.  This emulates the message and latency overhead of Paxos between replica-controllers and between active replicas, but Paxos with consistency guarantees is still under performance testing.  (2) Replica-controllers estimate  geo-distribution of requests based on local name servers' report of the number of lookups received by them; we plan to integrate an IP geo-location database for active replicas instead to report the request geo-distribution to replica-controllers.  (3) A local name server maintains load-induced latency estimates for each name server by querying them for their current load every 5 mins instead of tracking load-induced latency at name servers based on response time of past lookups ($\S$\ref{sec:routing_client_requests}).

@@

%In this version,  (1) we infer the geo-distribution of lookups for a name, earlier code relied on local name servers to report the number of lookups  they receive for a name to the replica-controllers. We plan to integrate an IP-geolocation database at name servers so that active replicas can directly report the geo-distribution of lookups. (2) Replication control parameter ($\beta$) is currently specified as a fixed configuration parameter and not calculated automatically based aggregate lookup and update rates across name servers.   (3)  A local name server maintains load-induced latency estimates for each name server by querying them for their current load every 5 minutes, instead of tracking load-induced latency at name servers based on response time of past lookups (Section \ref{sec:routing_client_requests}).

%The current version which implements Paxos between replica-controllers and active replicas to provide consistency guarantees,  is under testing phase. In addition, the current version also address following We also plan to add the following features to the current version:  (1) To infer the geo-distribution of lookups for a name, earlier code relied on local name servers to report the number of lookups  they receive for a name to the replica-controllers. We plan to integrate an IP-geolocation database at name servers so that active replicas can directly report the geo-distribution of lookups. (2) Replication control parameter ($\beta$) is currently specified as a fixed configuration parameter and not calculated automatically based aggregate lookup and update rates across name servers.   (3)  A local name server maintains load-induced latency estimates for each name server by querying them for their current load every 5 minutes, instead of tracking load-induced latency at name servers based on response time of past lookups (Section \ref{sec:routing_client_requests}).

%Some features of the implementation are still work-in-progress at this point. (1) To infer the geo-distribution of lookups for a name, we currently rely on local name servers to report the number of lookups  they receive for a name to the replica-controllers. We plan to integrate an IP-geolocation database at name servers so that active replicas can directly report the geo-distribution of lookups. (2) Replication control parameter ($\beta$) is currently specified as a fixed configuration parameter and not calculated automatically based aggregate lookup and update rates across name servers.   (3)  A local name server maintains load-induced latency estimates for each name server by querying them for their current load every 5 minutes, instead of tracking load-induced latency at name servers based on response time of past lookups (Section \ref{sec:routing_client_requests}).

%Some parts of the implementation are still work-in-progress at this point. (1) To infer the geo-distribution of lookups for a name, we currently rely on local name servers to report the number of lookups  they receive for a name to the replica-controllers. We plan to integrate an IP-geolocation database at name servers so that active replicas can directly report the geo-distribution of lookups. (2) Replication control parameter ($\beta$) is currently specified as a fixed configuration parameter and not calculated automatically based aggregate lookup and update rates across name servers.   (3)  A local name server maintains load-induced latency estimates for each name server by querying them for their current load every 5 minutes, instead of tracking load-induced latency at name servers based on response time of past lookups (Section \ref{sec:routing_client_requests}).

@@

%\textcolor{blue}{Local-name server maintains load-induced latency estimates by actively requesting the name servers for their current load once every 5 minutes. This approach adds a small overhead for our largest deployment of 80 name servers and 80 local name servers. To eliminate this overhead, we will implement the approach described in Section \ref{sec:routing_client_requests}, which is to estimate load-induced latency based on response time of past lookups.}

@@

%\subsection{Replica placement algorithm}
%
%
%\textbf{Resolver placement algorithm:} The resolver placement algorithm in \auspice\  proceeds in three steps: aggregation, voting, and replication.
%
%\emph{Aggregation}: The aggregation step is used to calculate the lookup rate and and the update rate  of name records.  To this end, the resolvers for a name record send the lookup and update rates for this name record to the replication controller  once every epoch.
%
%\emph{Voting}:  The geo-distribution of requests for a name record is obtained using votes sent by local name servers to the replication controllers. A vote consists of a tuple {(\textsf{namerecord}, \textsf{nameserverID}, \textsf{votecount}). The \textsf{nameserverID} is the ID of the name server closest to this local name server based on latency estimates. The \textsf{votecount} is equal to the number of requests for \textsf{namerecord} sent to name servers by this local name server since the last time the voting step was executed.
%
%\emph{Replication:}  This step executes at replication controller for a name record. Resolvers are selected based on lookup and update rates, and votes received in the past one hour using the algorithm in Section \ref{sec:heuristic}. Any change in the set of resolvers replicas since last execution of replication step is communicated to the new and the old set of resolvers. By default, all three steps are executed once every five minutes.

>>>>

We have implemented a prototype of the global name service with support for all of the functions described in Section \\ref{sec:MF} using \auspice. A service in \auspice\ is a resolver for a name (or GUID). Each resolver is replicated with primary and active replicas and the number and locations of these replicas is determined by the mapper. We have implemented both uncoordinated, heuristic algorithms as well as the coordinated, optimal placement algorithms as described in the previous two sections.

The name service ensures sequential consistency for each resolution service by establishing a total order across all writes to attributes keyed by the service's GUID. When an active replica receives a write to any GUID attribute, it initiates Paxos (unrelated to Paxos between primaries for placement decisions as in Section \\ref{sec:design}) and gets all other active replicas responsible for that GUID to agree on a sequence number for that write. A read request at a replica sees the result of the most recent committed write at that replica. A total ordering of writes at all replicas is insufficient to ensure the desirable property that replicas will {eventually} return the most current (in real time) network address of a mobile device  if no further updates take place (e.g., a mobile may issue an update at replica A and subsequently an update at replica B, but it is theoretically possible for the system to commit the latter before the former). To ensure this property in single-writer scenarios, a client includes a client-local sequence number to each write and the acceptors in Paxos ensure that they do not accept a proposed sequence number for a write $w_1$ if they have already accepted a write $w_2$ with a higher client-local sequence number, thereby causing the proposed write $w_1$ to fail to commit.

@@

%Some parts of the implementation are work in progress at this point. (1) Replica-controllers estimate  geo-distribution of requests based on local name servers' report of the number of lookups received by them; we plan to integrate an IP geo-location database for active replicas instead to report the request geo-distribution to replica-controllers.  (2) A local name server maintains load-induced latency estimates for each name server by querying them for their current load every 5 mins instead of tracking load-induced latency at name servers based on response time of past lookups  as described in Section \ref{sec:routing_client_requests}.

%\textbf{Evaluation version:} We have implemented a full-featured prototype of \auspice\ as described above, but our evaluation uses an earlier stable version of our code with some differences.  This evaluation version is implemented in Java with 22K lines of code, and is currently deployed  on Amazon EC2 for users to query via HTTP \cite{gnrswebsite}. This version differs from the described design as follows: (1) An update involves the set of message exchanges described in $\S$$\ref{sec:consistency}$ without assigning any update sequence numbers.  This emulates the message and latency overhead of Paxos between replica-controllers and between active replicas, but Paxos with consistency guarantees is still under performance testing.  (2) Replica-controllers estimate  geo-distribution of requests based on local name servers' report of the number of lookups received by them; we plan to integrate an IP geo-location database for active replicas instead to report the request geo-distribution to replica-controllers.  (3) A local name server maintains load-induced latency estimates for each name server by querying them for their current load every 5 mins instead of tracking load-induced latency at name servers based on response time of past lookups (Section \ref{sec:routing_client_requests}).

@@

%In this version,  (1) we infer the geo-distribution of lookups for a name, earlier code relied on local name servers to report the number of lookups  they receive for a name to the replica-controllers. We plan to integrate an IP-geolocation database at name servers so that active replicas can directly report the geo-distribution of lookups. (2) Replication control parameter ($\beta$) is currently specified as a fixed configuration parameter and not calculated automatically based aggregate lookup and update rates across name servers.   (3)  A local name server maintains load-induced latency estimates for each name server by querying them for their current load every 5 minutes, instead of tracking load-induced latency at name servers based on response time of past lookups (Section \\ref{sec:routing_client_requests}).

%The current version which implements Paxos between replica-controllers and active replicas to provide consistency guarantees,  is under testing phase. In addition, the current version also address following We also plan to add the following features to the current version:  (1) To infer the geo-distribution of lookups for a name, earlier code relied on local name servers to report the number of lookups  they receive for a name to the replica-controllers. We plan to integrate an IP-geolocation database at name servers so that active replicas can directly report the geo-distribution of lookups. (2) Replication control parameter ($\beta$) is currently specified as a fixed configuration parameter and not calculated automatically based aggregate lookup and update rates across name servers.   (3)  A local name server maintains load-induced latency estimates for each name server by querying them for their current load every 5 minutes, instead of tracking load-induced latency at name servers based on response time of past lookups (Section \\ref{sec:routing_client_requests}).

%Some features of the implementation are still work-in-progress at this point. (1) To infer the geo-distribution of lookups for a name, we currently rely on local name servers to report the number of lookups  they receive for a name to the replica-controllers. We plan to integrate an IP-geolocation database at name servers so that active replicas can directly report the geo-distribution of lookups. (2) Replication control parameter ($\beta$) is currently specified as a fixed configuration parameter and not calculated automatically based aggregate lookup and update rates across name servers.   (3)  A local name server maintains load-induced latency estimates for each name server by querying them for their current load every 5 minutes, instead of tracking load-induced latency at name servers based on response time of past lookups (Section \\ref{sec:routing_client_requests}).

%Some parts of the implementation are still work-in-progress at this point. (1) To infer the geo-distribution of lookups for a name, we currently rely on local name servers to report the number of lookups  they receive for a name to the replica-controllers. We plan to integrate an IP-geolocation database at name servers so that active replicas can directly report the geo-distribution of lookups. (2) Replication control parameter ($\beta$) is currently specified as a fixed configuration parameter and not calculated automatically based aggregate lookup and update rates across name servers.   (3)  A local name server maintains load-induced latency estimates for each name server by querying them for their current load every 5 minutes, instead of tracking load-induced latency at name servers based on response time of past lookups (Section \\ref{sec:routing_client_requests}).

@@

%\textcolor{blue}{Local-name server maintains load-induced latency estimates by actively requesting the name servers for their current load once every 5 minutes. This approach adds a small overhead for our largest deployment of 80 name servers and 80 local name servers. To eliminate this overhead, we will implement the approach described in Section \\ref{sec:routing_client_requests}, which is to estimate load-induced latency based on response time of past lookups.}

@@

%\subsection{Replica placement algorithm}
%
%
%\textbf{Resolver placement algorithm:} The resolver placement algorithm in \auspice\  proceeds in three steps: aggregation, voting, and replication.
%
%\emph{Aggregation}: The aggregation step is used to calculate the lookup rate and and the update rate  of name records.  To this end, the resolvers for a name record send the lookup and update rates for this name record to the replication controller  once every epoch.
%
%\emph{Voting}:  The geo-distribution of requests for a name record is obtained using votes sent by local name servers to the replication controllers. A vote consists of a tuple {(\textsf{namerecord}, \textsf{nameserverID}, \textsf{votecount}). The \textsf{nameserverID} is the ID of the name server closest to this local name server based on latency estimates. The \textsf{votecount} is equal to the number of requests for \textsf{namerecord} sent to name servers by this local name server since the last time the voting step was executed.
%
%\emph{Replication:}  This step executes at replication controller for a name record. Resolvers are selected based on lookup and update rates, and votes received in the past one hour using the algorithm in Section \\ref{sec:heuristic}. Any change in the set of resolvers replicas since last execution of replication step is communicated to the new and the old set of resolvers. By default, all three steps are executed once every five minutes.
